---
title: "p8106_hw1_yg2625"
author: "Yue Gu"
date: "March 3, 2019"
output: 
  pdf_document:
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(caret)
library(boot)
library(ISLR)
library(glmnet)
library(corrplot)
library(plotmo)
```

# Import data
```{r}
train_data = read.csv("./data/solubility_train.csv") %>% 
  janitor::clean_names()
test_data = read.csv("./data/solubility_test.csv") %>% 
  janitor::clean_names()
```

# (a) Fit a linear model using least squares on the training data and calculate the mean square error using the test data.
## Fit linear model on the training data
```{r}
fit_lm_tr = lm(solubility ~ .， data = train_data)
summary(fit_lm_tr)
```

## Calculate the mean square error using the test data
```{r}
pred_lm_tr = predict(fit_lm_tr, test_data)
mse_test = mean((pred_lm_tr - test_data$solubility)^2);mse_test
```
Hence, the MSE using test data is `r mse_test`.

# (b) Fit a ridge regression model on the training data, with lambda chosen by cross-validation. Report the test error.

## Fit ridge regression model on the training data
```{r}
train_data = na.omit(train_data)
x = model.matrix(solubility ~ ., train_data)[, -1]
y = train_data$solubility

ridge_mod = glmnet(x, y, alpha = 0, lambda = exp(seq(-5, 5, length = 500)))
mat_coef = coef(ridge_mod)
dim(mat_coef)

# Cross-validation
set.seed(1)
cv_ridge = cv.glmnet(x, y,
                     alpha = 0,
                     lambda = exp(seq(-5, 5, length = 500)),
                     type.measure = "mse")
plot(cv_ridge)

# Trace plot
plot_glmnet(ridge_mod, xvar = "rlambda")

# Predict response in final model
best_lambda = cv_ridge$lambda.min; best_lambda
pred_resp_ridge = predict(ridge_mod, s = best_lambda, newx = model.matrix(solubility ~ ., test_data)[, -1], type = "response")
mse_ridge = mean((pred_resp_ridge - test_data$solubility)^2); mse_ridge
```

Based on the result, the MSE for ridge regression is `r mse_ridge`.

# (c) Fit a lasso model on the training data, with lambda chosen by cross-validation. Report the test error, along with the number of non-zero coefficient estimates.

## Fit lasso model on the training data

